The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
editing section 3.2

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \arun{Give parameter values. Set
             minor ticks.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use
  thicker line width for the actual histogram.  Change legend to say
  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the
actual equation.  Also, why are two of the horizontal lines in the
bottom panel solid and one dashed?  What decides the style for each
line?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_I$) space.}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_I$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:MIhist}
 \end{figure}

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on  $M_I$, which are $K$-corrected $i^+$-band magnitudes from Subaru or from the PSF-matched CHFT $i^*$-band images.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
\rachel{Actually, is this the catalog entry called ``MI''?  If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit. We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_I<-22$, we are not affected by flux limit yet.

%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
and redo the volume limiting procedure.
We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin. This increases the sample size significantly, from 7,418 galaxies to 11,169. We call this sample \s$1$.

However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
We used the published result \citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
Therefore, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.

Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve. Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF \citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.

\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
 \hline
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
\label{table:GalaxyCounts}
\end{table}

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{SMF}
 \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
          a study of SMF in the same survey \citep{Tomczak_SMF}. At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range. The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
12\% of galaxies that pass our cuts do not have an associated postage stamp image.
Yet, we use the full $m_\text{F814W}\le23.5$ sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
%\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
%\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
Postage stamps may not exist because, given the size of the galaxy, the size of the postage stamp we want to draw around it (including enough blank space) intersects with the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this is an effect that is dominant at lower redshifts. 
Our completeness calculation is done at high redshifts and thus we believe that our conclusions are not affected by this bias.

@@

The functional forms for the (flux-limited) redshift distribution that we used in \S\ref{sub:overdensities} are not physically motivated. We fit them again to the  
redshift distribution of a volume-limited sample (\s$1$). Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0. This is the reason why in \S\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in \S\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_vollimited}
\end{figure}

@@

In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.

@@

An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of \cite{HS03} (hereafter HS03).
This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on \cite{BJ02}. Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities 
of the galaxies, which we will refer to as `ellipticities based on moments'.

\section{Results}
\label{S:results}
Having identified the overdense and underdense regions in a volume-limited sample (\S\ref{sub:overdensities}, \S\ref{sub:volumelimiting}), we will now see in this section if the morphological
parameters of the galaxies, listed in \S\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
\begin{enumerate}
 \item no redshift evolution of luminosity cut $(\s1)$,
 \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
 \item impose stellar mass cuts instead of luminosity $(\s3)$
\end{enumerate}
and we will present our results in each of the 3 cases.

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \arun{Give parameter values. Set
             minor ticks.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use
  thicker line width for the actual histogram.  Change legend to say
  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the
actual equation.  Also, why are two of the horizontal lines in the
bottom panel solid and one dashed?  What decides the style for each
line?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$). \rachel{What
       redshift range?}}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of absolute magnitude $M_I$ for various
     flux-limited samples are plotted together. The vertical line
     corresponds to our luminosity cut of $-20.8$, brighter than which
     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
     galaxies in the $m_\text{F814W}<25.2$ sample.
   \rachel{Is this plot and the numbers in the caption for
     $0.8<z<0.85$ only?  This is currently implied by the text.  If
     that is true, then please fix the figure and caption to say
     this.  If that is wrong, then please fix the text.}}
   \label{fig:MIhist}
 \end{figure}

\subsection{Volume limiting}
\label{sub:volumelimiting}

COSMOS is a flux-limited survey and is therefore affected by Malmquist
bias, with the galaxy samples at higher redshift being intrinsically
brighter on average.  
Our analysis involves comparing galaxies in different redshift slices
to identity significant differences in morphology that arise due to
morphology-density correlations.  Such an analysis would be very
difficult with a flux-limited sample because there would be some
variation in morphology with redshift just due to the intrinsic change
in the sample properties.  For a fair comparison, we must restrict
ourselves to galaxies that are bright enough that they would be
observed at all redshifts that we consider, which is achieved by
volume-limiting the sample.  We consider three different ways of
carrying out this process, which results in three different galaxy
sample selections, all of which we will use in the remainder of the
analysis.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}

Our first approach is to generate a volume-limited sample that is
complete up to $z=1$, by applying a cut on luminosity such that only
galaxies instrinsically brighter than a certain threshold (determined
in detail below) is considered. This threshold is set on the
$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
photometry catalog.   The joint distribution of $m_\text{F814W}$ and
$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
Since the parent sample contains fainter galaxies and is quite
complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
have fainter flux limits, to see where the $m_\text{F814W}<23.5$
sample that we want to use for our tests is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}
At $M_I\sim-22.0$, the
$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
redshift bin was found to be only moderately overdense, so we choose
to disregard this region for the rest of the analysis, and instead
restrict to $z<0.85$, which is advantageous because it allows us to
choose a somewhat fainter intrinsic luminosity limit for the
analysis.  We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
of this work.

However, previous studies
\citep[e.g.,][]{2003A&A...401...73W,2005ApJ...622..116G,2006ApJ...647..853W,Faber2007}
have shown that galaxy intrinsic luminosities evolve with
redshift. Thus, we should also let the luminosity cut that we apply to
volume-limit the sample evolve with redshift. 
Unfortunately, the majority of the published work on evolution of the
luminosity function uses $B$ and $V$ band data, and it is not apparent
that the results should be the same in a redder passband like $I$.  
We use the results from \cite{Faber2007} for the evolution of
$B$-band magnitudes from the DEEP2 and COMBO-17 surveys, which is $
\Delta M_B^* \sim -1.23$ mag per unit redshift (with the sign
indicating that galaxies were intrinsically brighter in the past), for a combined sample
of blue and red galaxies. 
Typically, estimates of evolution in the much redder $K$ band are less
than the estimates of evolution in $B$ and $V$ bands. (\rachel{Please
  include a citation for this statement.}) 
Assuming that the evolution is a smooth function of the wavelength,
the evolution in $I$-band should be in between $B$ and $K$ band. 
Therefore, by considering no evolution (a lower limit) as in our \s$1$, and a second
sample \s$2$ constructed using the $B$-band evolution (as an upper
bound on the $I$-band evolution), we can assume that these two samples
bracket reality, which should be somewhere in between.

Thus, \s$2$ is constructed by letting the luminosity cut evolve,
starting from $M_I = -20.8$ (same as in \s$1$) for the $0.8<z\le0.85$
bin.  The cut values for the other bins are defined by allowing $1.23$
magnitudes of evolution to fainter magnitudes as a function of
redshift (evaluated using the bin centers).  Because of the sign of
redshift evolution, \s$2$ includes  more galaxies.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They considered for this work a single stellar
population (\rachel{What do you mean by a single stellar population?})
following a Chabrier IMF \citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
 \hline
\end{tabular}
\caption{List of different redshift bins, their environmental
  classification and the number of galaxies per redshift bin for
  volume-limited samples constructed in three different ways: using a
  hard luminosity cut (\s$1$), using a redshift-dependent luminosity cut (\s$2$) and using stellar-mass cuts (\s$3$).}
\label{table:GalaxyCounts}
\end{table}

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{SMF}
 \caption{Stellar mass distribution for various flux-limited samples
   are shown in three redshift ranges as separate panels. The redshift
   bins have been chosen to facilitate the comparison with  
          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
          distributions are the same for various flux limits,
          indicating that the samples are complete in that mass
          range. The curves begin to deviate at low masses due to
          incompleteness coming from the flux limit.  The point at
          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

There is one subtlety in our method used for estimating
completeness. We have used the full $m_\text{F814W}\le23.5$ sample
for identifying
overdensities and for the completeness calculations that motivated our
definitions of volume-limited samples. (\rachel{Do the numbers in the
  table include the full sample or just the subsample with postage stamps?}) However, in the rest of this
paper, we analyse only those galaxies for which there are postage stamp
images used to create weak lensing simulations, in part because this is the
sample for which fits to \sersic\ profiles were carried out, which is a
requirement for our morphology analysis.  
12 per cent of the galaxies that pass our cuts do not have an
associated postage stamp image.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
some blank space) intersects the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
It is commonly the case that  galaxies that are nearby and
intrinsically very bright do not have postage stamps associated with
them, an effect that is dominant at lower redshifts (and is part of
our reason for excluding $z<0.3$). 
Our completeness calculation is done at high redshifts, and thus we
believe that our conclusions are not affected by this bias.

@@

The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We fit them again to the  
redshift distribution of a volume-limited sample
(\s$1$). Fig.~\ref{fig:redshift_vollimited} shows that when we do
this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
increase and are within the $[-0.1, 0.1]$ range that we have defined
as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior in
Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

%In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.

@@

An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in Sec.~2.4 of \cite{HS03} (hereafter HS03).
This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
covariances of the measured object and PSF respectively, described in Sec.~2.1 of HS03, which is in turn based on \cite{BJ02}. Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities 
of the galaxies, which we will refer to as `ellipticities based on moments'.

\section{Results}
\label{S:results}
Having identified the overdense and underdense regions in a volume-limited sample (Sec.~\ref{sub:overdensities}, Sec.~\ref{sub:volumelimiting}), we will now see in this section if the morphological
parameters of the galaxies, listed in Sec.~\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
\begin{enumerate}
 \item no redshift evolution of luminosity cut $(\s1)$,
 \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
 \item impose stellar mass cuts instead of luminosity $(\s3)$
\end{enumerate}
and we will present our results in each of the 3 cases.
